AIS

### 2023-04-21 02_AIS.Rmd
Added code for measuring distance

library(tidyverse)
library(sf)

@@

  st_intersection(x, y_subset,...)
}
```

@@

```{r}
##################################
# Create 10 km buffer around buoys (taken from M. McKenna's code)
# Should be malleable for each buoy's number to easily plug in.
##################################
trk8 <- tracks %>% 
  dplyr::filter(station == "8") %>%
  st_as_sf(coords= c("Longitude", "Latitude"), crs=4326, remove=F)

@@

### Crop full AIS to 10km buffer around drift 8 ###
AIS_crop <- st_crop(x = AIS_sf, y = buff)

# Intersect buffer with AIS. Starting this on first 10 rows to see how slowly it goes. 
## FIX ME
#inters <- st_intersection(buff, AIS_crop[1:140,])

#Another way to view AIS points that fall within buffer. DOES NOT consider time.
AIS_within_buff <- AIS_crop[buff,]
by <- join_by(closest(UTC >= BaseDateTime))
trk_AIS <- left_join(as.data.frame(trk8), as.data.frame(AIS_within_buff), by)

inters <- st_intersection_faster(buff, AIS_crop[1:140,])
inters2 <- st_intersection_faster(buff, AIS_crop[141:200,])
inters3 <- st_intersection_faster(buff, AIS_crop[201:300,])

```
```{r}
# Plot showing 10km buffer around drift 8
#tmap_mode("plot")
#tm_shape(buff) + tm_symbols(col = "blue", border.col = NA) +
#  tm_shape(trk) + tm_dots(col = "red")
```

```{r}
# Plot
ggplot(tracks_SS_08, aes(x = long, y = lat.x)) + geom_point() 
 + geom_sf(data = bbox8, aes(col = "red"))

# Plot showing AIS bounding box around drift 8 tracks
ggplot() + geom_sf(data = trk_AIS, color = "red")
ggplot() + geom_sf(data = buff[lgth,] ,color = "red")

@@

>>>>

library(tidyverse)
library(sf)
library(gganimate)
#install.packages("remotes")
#remotes::install_github("skgrange/gissr")
#devtools::install_github("skgrange/gissr")
library(gissr)

@@

  st_intersection(x, y_subset,...)
}

```

@@

```{r}
##################################
# Create 10 km buffer around buoys (taken from M. McKenna's code)
# Should be malleable for each buoy's number to easily plug in.
##################################
tracks <- readRDS("data-raw/tracks.rda")

trk8 <- tracks %>% 
  dplyr::filter(station == "8") %>%
  st_as_sf(coords= c("Longitude", "Latitude"), crs=4326, remove=F)

@@

### Crop full AIS to 10km buffer around drift 8 ###
AIS_crop <- st_crop(x = AIS_sf, y = buff)
```

```{r}
# Intersect buffer with AIS. Starting this on first 10 rows to see how slowly it goes. 
## FIX ME
#inters <- st_intersection(buff, AIS_crop[1:140,])

#Another way to view AIS points that fall within buffer. DOES NOT consider time.
AIS_within_buff <- AIS_crop[buff,]
f <- buff[AIS_within_buff,]
by <- join_by(closest(UTC >= BaseDateTime))

d <- full_join(buff, as.data.frame(AIS_within_buff), by)

e <- d[!duplicated(d[c('BaseDateTime')]),]

trk_AIS <- left_join(as.data.frame(trk8), as.data.frame(AIS_within_buff), by)

proj4string <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
trk_AIS_sf <- trk_AIS %>% st_as_sf(coords = c("Longitude", "Latitude"), crs=projcrs, remove=F)# %>%
   st_set_crs(4326)
trk_AIS_sf <- st_transform(trk_AIS_sf, crs = 4326)

#inters <- st_intersection_faster(buff, AIS_crop[1:140,])
#inters2 <- st_intersection_faster(buff, AIS_crop[141:200,])
#inters3 <- st_intersection_faster(buff, AIS_crop[201:300,])

#Another way to view AIS points that fall within buffer. DOES NOT consider time.

st_is_within_distance(AIS_crop, pois, dist = 10000)
st_distance(AIS_crop, pois, dist_fun = 10000)

st_set_geometry(AIS_crop, value = NULL)
st_set_geometry(pois, value = NULL)

AIS_crop <- as_Spatial(AIS_crop)
pois <- as_Spatial(pois)
AIS_within_buff <- as_Spatial(AIS_within_buff)
z <- sp_distance(AIS_crop, pois, features = TRUE, unit = "km")

data_places <- pois@data
data_places$distance <- sp_distance(AIS_within_buff, pois, features = TRUE, unit = "km")
View(data_places)

rgeos::gWithinDistance(AIS_crop, pois, features = TRUE, dist = 10000)
```
```{r}
# For each row in AIS df,
  # calculate distance to closest drift
  # return smallest distance
  # attach column to df

# 
(geosphere::distHaversine(AIS_within_buff[9:20,], pois))/1000
```

```{r}
# Plot showing 10km buffer around drift 8
#tmap_mode("plot")
#tm_shape(buff) + tm_symbols(col = "blue", border.col = NA) +
#  tm_shape(trk) + tm_dots(col = "red")
```

plots
```{r}
# Plot
ggplot(tracks_SS_08, aes(x = long, y = lat.x)) + geom_point() 
 + geom_sf(data = bbox8, aes(col = "red"))

# Plot showing AIS bounding box around drift 8 tracks
ggplot() + geom_sf(data = trk_AIS_sf, color = "red")
ggplot() + geom_sf(data = buff[lgth,] ,color = "red")

@@

p <- ggplot() + geom_sf(data = buff, mapping = aes(x=Longitude,y=Latitude)) +
  geom_point(data = AIS_within_buff, mapping = aes(x=LON,y=LAT, group = VesselName), color = "red")

anim <- p +
  transition_reveal(along = BaseDateTime)+
  ease_aes('linear')+
  #shadow_wake(0.1) +
  ggtitle("Date: {frame_along}")

animate(anim, nframes = 180, fps = 3)
```
